Social Housing in Toronto

### 2024-04-22 paper/paper.qmd
commit

# Extract relevant columns with adjusted column names
year_quarter <- analysis_data$Quarter_Year
household_no_dependents <- analysis_data$Household_no_dependents
household_with_dependents <- analysis_data$Household_with_dependents

# Create a data frame
plot_data <- data.frame(Year_Quarter = year_quarter,
                        household_no_dependents = household_no_dependents,
                        household_with_dependents = household_with_dependents)

>>>>

# Extract relevant columns with adjusted column names
year_quarter <- analysis_data$Quarter_Year
tes1 <- analysis_data$Household_no_dependents
test2 <- analysis_data$Household_with_dependents

# Create a data frame
plot_data <- data.frame(Year_Quarter = year_quarter,
                        test1 = household_no_dependents,
                        test2 = household_with_dependents)
